EU-Circle Case study 5

### 2016-12-07 EU-Circle/eu-circle_case-study-5.Rmd

>>>>

## Analysis: precipitation

Data from ECA&D: precipitation. Snow depth?

```{r}
library(esd)
ss <- select.station(param='precip',cntr='Germany',alt=250,nmin=75)
map(ss,new=FALSE)
Y <- station(ss)
Y <- subset(Y,it=c(1950,2015))
diagnose(Y)
nv <- apply(coredata(Y),2,'nv')
Y <- subset(Y,is=nv > 24000)
```

```{r}
y <- subset(Y,is=1)
coredata(y) <- rowMeans(coredata(Y))
attr(y,'location') <- 'German higher elevation'
attr(y,'longitude') <- mean(lon(Y))
attr(y,'latitude') <- mean(lat(Y))
attr(y,'altitude') <- min(alt(Y))
plot(y)
lines(trend(y),lty=2)
grid()
```

Area total precipitation from gridded EOBS.

```{r}
rr <- retrieve('data.ECAD/rr_0.25deg_reg.nc',lon=range(lon(Y)),lat=range(lat(Y)))
map(rr,new=FALSE)
Arr <- aggregate.area(rr)
plot(rr,new=FALSE)
```

Wet day mean and frequency

```{r}
mu <- annual(rr,FUN='wetmean')
fw <- annual(rr,FUN='wetfreq')
MU <- aggregate.area(mu,FUN='mean')
FW <- aggregate.area(fw,FUN='mean')
plot(MU,new=FALSE)
lines(trend(MU),lty=2)
grid()
plot(FW,new=FALSE)
grid()
lines(trend(FW),lty=2)
```

Plot the probability of more than 50mm/day

```{r}
Pr.50 <- FW*exp(-50/MU)
plot(Pr.50)
lines(trend(Pr.50),lty=2)
grid()
```

## Analysis: temperature

Check for melting.

```{r}
ss <- select.station(param='tn',cntr='Germany',alt=500,nmin=75)
map(ss)
X <- subset(station(ss),it=month.abb[1:4])
diagnose(X)
X <- subset(X,it=c(1940,2015))
```

```{r}
tnx <- annual(X,FUN='max',nmin=100)
plot(tnx,new=FALSE)
grid()
```
